JWST Noise Floor I: Systematic Error Sources with JWST NIRCam Time Series

### 2020-05-08 ms.tex
added a plot showing the noise contributions for a generic source

\subsection{Row-by-Row Subtraction}\label{sec:photRowByRow}

@@

\subsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
A slight modification to the above strategy is to average each amplifier individually.
This takes care of any differences between amplifiers.
This individual amplifier dramatically decreases the errors.
The standard deviations of the background-subtracted photometry range from 2,540 to 3,300 DN or 65 to 85 ppm across detectors.
Therefore, this simple approach can dramatically decrease the 1/f noise to well below the photon limit.
This is possible for Weak Lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).

\subsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}

@@

>>>>

\subsubsection{Row-by-Row Subtraction}\label{sec:photRowByRow}

@@

\subsubsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
A slight modification to the above strategy is to average each amplifier individually.
This takes care of any differences between amplifiers.
This individual amplifier dramatically decreases the errors.
The standard deviations of the background-subtracted photometry range from 2,540 to 3,300 DN or 65 to 85 ppm across detectors.
Therefore, this simple approach can dramatically decrease the 1/f noise to well below the photon limit.
This is possible for Weak Lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).

\subsubsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}

@@

So far, we have discussed the magnitude of correlated read noise on an integration-by-integration basis, but it is also helpful to see its impact on the transit depth or eclipse depth of an exoplanet.
For context, the features size of atmospheric signatures on archetypical planets are expected to be $\sim$300 ppm for hot Jupiters and Neptunes but only 10 ppm for cool Super-Earths like K2-3 b \citep{greene2016jwst_trans}.
The 
 with clouds have molecular features of $\sim$300 ppm, most easily-observable planets, such as hot Jupiters, are expected to have molecular atmospheric features of $\sim$200 to $\sim$500 ppm \citep{schlawin2018JWSTforecasts,greene2016jwst_trans}.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.59\columnwidth]{generic_src_errors.pdf}
\caption{Bright sources, where only a handful of groups per integration are possible without saturation, can be dominated by read noise due to correlated errors and small photon noise.
}\label{fig:genericSourceErrorContrib}
\end{figure}
